Introduction to Natural Language Processing

### 2007-07-12 slides/baypiggies.tex
fixed size of python snippets
svn/trunk@4880

\begin{frame}[fragile]
  \frametitle{Classifying in NLTK}
  \begin{itemize}
    \item Classifiers are applied to \emph{featuresets}:
\begin{alltt}\small
>>> animal = dict(fur=True, legs=4, 
                  size='large', spots=True)
>>> my_classifier.classify(animal)
'leopard'
\end{alltt}
    \item Features are found with a \emph{feature extractor}:
\begin{alltt}\small
>>> def document_features(document):
...     return dict([('contains-word(%s)'%w,True) 
...                  for w in document])
\end{alltt}
    \item Training:
\begin{alltt}\small
>>> labeled_featuresets = [(document_features(doc), label)
..       .                 for (doc, label) in labeled_docs]
>>> classifier = NaiveBayesClassifier.train(labeled_docs)
\end{alltt}

>>>>

\begin{frame}[fragile]
  \frametitle{Classifying in NLTK}
  \begin{itemize}
    \item Classifiers are applied to \emph{featuresets}:
{\small\begin{alltt}
>>> animal = dict(fur=True, legs=4, 
                  size='large', spots=True)
>>> my_classifier.classify(animal)
'leopard'
\end{alltt}}
    \item Features are found with a \emph{feature extractor}:
{\small\begin{alltt}
>>> def document_features(document):
...     return dict([('contains-word(%s)'%w,True) 
...                  for w in document])
\end{alltt}}
    \item Training:
{\small\begin{alltt}
>>> train = [(document_features(doc), label)
..           for (doc, label) in labeled_docs]
>>> classifier = NaiveBayesClassifier.train(train)
\end{alltt}}
